Component response rate variation drives stability in large complex systems

### 2018-06-01 notebook/SI.Rmd
Add more notebook files; final draft edits

---
title: "Component response rate variation drives stability in large complex systems"
subtitle: "Supplemental Information"
author: "Brad Duthie"
date: Biological and Environmental Sciences, University of Stirling, Stirling, UK,
  FK9 4LA alexander.duthie@stir.ac.uk
bibliography: references.bib
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage[utf8]{inputenc}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
link-citations: yes
linkcolor: blue
csl: nature.csl
biblio-style: apalike
---

@@

- [Code and simulations underlying Fig. 1](#Fig1) 
- [Code and simulations underlying Fig. 2](#Fig2) 
- [Stability across increasing $S$](#IncrS) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Different connectance (C) values](#connectance)
    - [C = 0.3](#connect3)
    - [C = 0.5](#connect5)
    - [C = 0.7](#connect7)
    - [C = 0.9](#connect9)
- [Different distributions of $\gamma$](#gam_dist)
- [Feasilbility of complex systems](#Feasibility) 
- [Genetic algorithm](#ga)

>>>>

---
title: "Component response rate variation drives stability in large complex systems"
author: "Brad Duthie"
date: Biological and Environmental Sciences, University of Stirling, Stirling, UK,
  FK9 4LA alexander.duthie@stir.ac.uk
output:
  pdf_document:
    fig_caption: yes
  html_document: default
  word_document:
    fig_caption: yes
    pandoc_args:
    - --csl
    - evolution.csl
    reference_docx: docx_template.docx
bibliography: references.bib
header-includes:
- \usepackage{amsmath}
- \usepackage{natbib}
- \usepackage{lineno}
- \usepackage[utf8]{inputenc}
- \linenumbers
- \bibliographystyle{amnatnat}
linestretch: 1
link-citations: yes
linkcolor: blue
csl: nature.csl
subtitle: Supplemental Information
biblio-style: apalike
---

@@

- [Code and simulations underlying Fig. 1](#Fig1) 
- [Code and simulations underlying Fig. 2](#Fig2) 
- [Stability across increasing $S$](#IncrS) 
- [Stability of ecological networks](#ecological) 
    - [Competitor networks](#competition) 
    - [Mutualist networks](#mutualism) 
    - [Predator-prey networks](#pred-prey) 
- [Different connectance (C) values](#connectance)
    - [C = 0.3](#connect3)
    - [C = 0.5](#connect5)
    - [C = 0.7](#connect7)
    - [C = 0.9](#connect9)
- [Different distributions of $\gamma$](#gam_dist)
- [Genetic algorithm](#ga) 
- [Feasilbility of complex systems](#Feasibility)
